---
title: "Car Weight and Fuel Efficiency"
subtitle: "A look at mtcars"
author: "Hein"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(plotly)
```

## The data

- `mtcars`: 32 cars from the 1974 *Motor Trend* magazine
- Question: do heavier cars use more fuel?
- Each point is one car. Hover over a point to see which car it is.

## Weight vs. miles per gallon

```{r plot}
cars <- mtcars
cars$model <- rownames(cars)
cars$cyl <- factor(cars$cyl)

plot_ly(cars, x = ~wt, y = ~mpg, color = ~cyl,
        type = "scatter", mode = "markers",
        marker = list(size = 11, opacity = 0.8),
        text = ~paste0("<b>", model, "</b><br>",
                       "Weight: ", wt * 1000, " lbs<br>",
                       "MPG: ", mpg, "<br>",
                       "Horsepower: ", hp),
        hoverinfo = "text") %>%
  layout(xaxis = list(title = "Weight (1000 lbs)"),
         yaxis = list(title = "Miles per gallon"),
         legend = list(title = list(text = "Cylinders")))
```

## What it shows

- Heavier cars get fewer miles per gallon.
- 4-cylinder cars cluster at light weight and high MPG.
- 8-cylinder cars are the heaviest and use more fuel.
- Click a legend item to hide or show that group.

## Thank you